Follow-up Samples

### 2017-03-31 results/tables/Table1.Rmd

---
title: ""
output: pdf_document
---

@@

ft1 <- cbind(Group = c("Normal", "Adenoma", "SRN", "Carcinoma"), ttemptable$Dx_Bin, ttemptable$Age, ttemptable$Gender_f, 
             ttemptable$BMI, ttemptable$White)

@@

colnames(ft1) <- c("Group", "n", age_label, "Gender (F%)", bmi_label, "Caucasian (%)")

>>>>

---
title: ""
output: pdf_document

---

@@

ft1 <- cbind(Group = c("Normal", "Adenoma", "Advanced Adenoma", "Carcinoma"), ttemptable$Dx_Bin, ttemptable$Age, ttemptable$Gender_f, 
             ttemptable$BMI, ttemptable$White)

@@

colnames(ft1) <- c("Group", "n", age_label, "Sex (%F)", bmi_label, "Caucasian (%)")

### 2017-03-31 results/tables/Table2.Rmd
edits prior to Amanda suggestions

ft1 <- cbind(Group = c("Adenoma", "SRN", "Carcinoma"), ttemptable$Dx_Bin, ttemptable$Age, ttemptable$Gender_f, 
             ttemptable$BMI, ttemptable$White)

ft1 <- cbind(Group = c("Normal", "Adenoma", "SRN", "Carcinoma"), ttemptable$Dx_Bin, ttemptable$Age, ttemptable$Gender_f, 
             ttemptable$BMI, ttemptable$White)

>>>>

ft1 <- cbind(Group = c("Adenoma", "Advanced Adenoma", "Carcinoma"), ttemptable$Dx_Bin, ttemptable$Age, ttemptable$Gender_f, 
             ttemptable$BMI, ttemptable$White)

### 2017-03-31 submission/supplemental_outline_20161024.Rmd

**Table S2: Summary of OTUs in Adenoma, SRN, and Carcinoma Models**

@@

adn_varsMDA <- read.csv('../data/process/tables/adn_reduced_crc_model_top_vars_MDA_Summary.csv', header = T, stringsAsFactors = F)

@@

# Create MDA vectors
adn_MDA <- filter(adn_varsMDA, variable %in% common_vars) %>% slice(match(common_vars, variable)) %>% select(mean_MDA)
srn_MDA <- filter(srn_varsMDA, variable %in% common_vars) %>% slice(match(common_vars, variable)) %>% select(mean_MDA)
crc_MDA <- filter(crc_varsMDA, variable %in% common_vars) %>% slice(match(common_vars, variable)) %>% select(mean_MDA)

st2 <- select(common_vars_summary, otu) %>% 
  mutate(Tax = gsub("_unclassified", "", common_vars_summary$lowest_ID)) %>% 
  mutate(adn_MDA = adn_MDA$mean_MDA, srn_MDA = srn_MDA$mean_MDA, crc_MDA = crc_MDA$mean_MDA) %>% 
  arrange(desc(adn_MDA), desc(srn_MDA), desc(crc_MDA))

>>>>

**Table S2: Summary of OTUs in Adenoma, Advanced Adenoma, and Carcinoma Models**

@@

adn_varsMDA <- read.csv('../data/process/tables/adn_reduced_model_top_vars_MDA_Summary.csv', header = T, stringsAsFactors = F)

@@

# Create MDA vectors
adn_MDA <- filter(adn_varsMDA, otu %in% common_vars) %>% slice(match(common_vars, otu)) %>% select(median_MDA)
srn_MDA <- filter(srn_varsMDA, otu %in% common_vars) %>% slice(match(common_vars, otu)) %>% select(median_MDA)
crc_MDA <- filter(crc_varsMDA, otu %in% common_vars) %>% slice(match(common_vars, otu)) %>% select(median_MDA)

st2 <- select(common_vars_summary, otu) %>% 
  mutate(Tax = gsub("_unclassified", "", common_vars_summary$lowest_ID)) %>% 
  mutate(adn_MDA = adn_MDA$median_MDA, srn_MDA = srn_MDA$median_MDA, crc_MDA = crc_MDA$median_MDA) %>% 
  arrange(desc(adn_MDA), desc(srn_MDA), desc(crc_MDA))
